Biodegradable alternatives to plastic mesh bags conventionally used in freshwater

### 2023-08-11 Rdocs/ManuscriptLPP.Rmd
changes made during meeting with Manny

#bag type barplot function:
#PARAMS: 
  #index(string): a string specifying the desired index

bt_barplot <- function(index){
  #calculate mean and standard error of chosen index
  new_tbl <- LPP_FullData%>%
  filter(is.na(material) == FALSE)%>% #remove na values from material before calculations
    group_by(material) %>% #group by material
    mutate(index_se = sd(get(index), na.rm = T)/sqrt(n())) %>% # calc SE
    summarise(index = mean(get(index), na.rm = T), index_se = mean(index_se)) #summarise into mean

  ggplot(new_tbl, aes(x = reorder(material, -index, sum), y = index)) +
    geom_col(aes(fill = reorder(material, -index, sum))) +
    geom_errorbar(aes(ymin = index - 2*index_se, ymax = index + 2*index_se)) +

    theme_bw() +
    scale_fill_viridis_d(begin = 0.1, end = 0.9)+
    theme_rafa(base_size = 15) +
    theme(axis.text.x = element_text(angle = -15, vjust = 0.5))+
    labs(x = "material", title = "Diversity Index by Bag material", y = paste(index),
         fill = "material")
}

@@

#PCA plot:----
#dotplot between pc1 and pc2, with % explained variance annotated in axis labels
ggplot(data = LPP_FullData, aes(x = PC1, y = PC2, fill = material)) +
  geom_point(shape = 21, size = 2.5) + 
geom_abline(slope = 0, intercept = 0, linetype = 2) +
  geom_vline(xintercept = 0, linetype = 2) +

@@

#screeplot----
fviz_eig(taxaCount_PCA) + theme_rafa(base_size = 16)
```

>>>>

#bag type barplot function:
#PARAMS: 
  #index(string): a string specifying the desired index
bt_barplot <- function(index){
  #save index as character
  char_index <- index
  #calculate mean and standard error of chosen index
  new_tbl <- LPP_FullData%>%
  filter(is.na(material) == FALSE)%>% #remove na values from material before calculations
    group_by(material) %>% #group by material
    mutate(index_se = sd(get(index), na.rm = T)/sqrt(n())) %>% # calc SE
    summarise(index = mean(get(index), na.rm = T), index_se = mean(index_se)) #summarise into mean

  ggplot(new_tbl, aes(x = reorder(material, -index, sum), y = index)) +
    geom_col(aes(fill = reorder(material, -index, sum))) +
    geom_errorbar(aes(ymin = index - 2*index_se, ymax = index + 2*index_se)) +
   # geom_text(aes(x = material, y = 0.5 + index, label = diversity_tukeys$char_index$groups$groups)) +

    theme_bw() +
    scale_fill_viridis_d()+
    theme_rafa(base_size = 15) +
    theme(axis.text.x = element_text(angle = -15, vjust = 0.5))+
    labs(x = "material", title = "Diversity Index by Bag material", y = paste(index),
         fill = "material")
}

@@

#PCA plot:----
#prin comp correl plot for all components
corrplot(taxa_ct_PCA$rotation)

#dotplot between pc1 and pc2, with % explained variance annotated in axis labels
ggplot(data = LPP_FullData, aes(x = PC1, y = PC2, fill = material)) +
  geom_point(shape = 21, size = 2.5) + 
geom_abline(slope = 0, intercept = 0, linetype = 2) +
  geom_vline(xintercept = 0, linetype = 2) +
  facet_wrap(~date) +

@@

#screeplot----
fviz_eig(taxa_ct_PCA) + theme_rafa(base_size = 16)

ggplot(LPP_FullData, aes(x = sqrt(MidgeFlies))) +
  geom_histogram()
```
